\documentclass[12pt]{WHOIletter}
\usepackage[margin=0.5in]{geometry}  % Sets all margins to 1 inch
\WHOIname{Brynnydd Hamilton}
\position{PhD Candidate}
\officenum{21}
\email{brynnydd.hamilton@whoi.edu}
\usepackage{graphicx}

\begin{document}

\begin{letter}{
Paleoclimatology and Paleoceanography \\
Editors of {\it Paleoceanography and Paleoclimatology} \\
}
\opening{Dear Editors of {\it Paleoceanography and Paleoclimatology},} 

Please find under this cover a manuscript entitled, ``Amplified North Atlantic Little Ice Age cooling inferred from inversion of benthic foraminiferal records,'' by Brynnydd Hamilton, Geoffrey Gebbie, Delia Oppo, and Wanyi Lu. Reconstructions of global and North Atlantic sea surface temperature cooling from the Medieval Climate Anomaly to the Little Ice Age have differed on their timing, magnitude, and spatial extent. This manuscript details an inverse approach to inferring Little Ice Age sea surface temperatures from benthic foraminiferal records. We present a methodology that significantly expands on prior inverse methodologies, and use it to estimate high-latitude North Atlantic sea surface temperatures over the past 1000 years. We find a LIA cooling of 0.41 $\pm$ 0.13 K cooling from 1140-1880 CE, which corroborates planktonic sea surface temperature estimates, and opposes reanalysis products' estimates of a dampened Little Ice Age.

This manuscript is suitable for publication in \textit{Paleoceanography and Paleoclimatology} due to its focus on reconstructing Common Era sea surface temperatures. It expands upon prior methodologies that were previously presented in \textit{Paleoceanography and Paleoclimatology} such as ``Inferring surface water equilibrium calcite $\delta^{18}$O during the last
deglacial period from benthic foraminiferal records: Implications for ocean circulation'' by Daniel E. Amrhein et al (2015).

This manuscript is over the 25 Publication Unit (PU) limit of \textit{Paleoceanography and Paleoclimatology} by 3 PU. However, we believe that this excess is warranted, as this work both presents new methodologies, applies them to new datasets, and interprets the results in their paleoceanographic context. 

This manuscript represents a mature work, and has been improved via a poster presentation at the American Geophysical Union's (AGU) 2022 Fall Meeting, as well as an oral presentation at the AGU 2024 Fall Meeting. In addition, this research has been carried out as graduate work, and has been presented to a thesis committee with Massachusetts Institute of Technology (MIT) and Woods Hole Oceanographic Institution (WHOI) representation. Feedback has been incorporated from all venues, acting to strengthen and develop the methods and findings. 

Thank you for considering this work for publication, and your attention.

\closing{Sincerely,}
\WHOIname\\PhD Candidate\\Woods Hole Oceanographic Institution

\end{letter}
\end{document}

% Spell check & quality check:
% detex file.tex | aspell list | sort | uniq
%
% QC:
% detex file.tex > text.txt
% diction, style, word_dupe, word_passive, word_weasel
%

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:
